	
\section{A Call To Action}

{\fontsize{11pt}{11pt}\selectfont
	I don't want to run a business. I don't want to manage or profit from
	anyone. I should like to help everyone - if possible - Man, Woman -
	young - old. We all want to help one another. Human beings are like
	that. We want to live by each other's happiness - not by each other's
	misery. We don't want to hate and despise one another. In this world
	there is room for everyone. And the good earth is rich and can provide
	for everyone. This way of life can be free and beautiful... but we have
	lost the way.
	
	Greed has poisoned our souls, has barricaded the world with hate, has
	drone-striked us into misery and bloodshed. We have developed speed, but
	we have shut ourselves in. The robotics that gives abundance has left us in
	want. Our knowledge has made us cynical. Our cleverness, hard and
	unkind. We think too much and feel too little. More than markets we need
	humanity. More than profitability we need kindness and gentleness.
	Without these qualities, life will be violent and all will be lost....
	
	The internet and the smartphone have brought us closer together. The
	very nature of these inventions cries out for the goodness in humanity -
	cries out for universal kinship - for the unity of us all. Even now my
	words could reach millions throughout the world - millions of
	despairing men, women, and little children - victims of a system that
	makes us choose either wage slavery or homeless destitution.
	
	To those who can hear me, I say - do not despair. The misery that is now
	upon us is but the passing of greed - the bitterness of those who fear
	the way of human progress. The rise of automation has taken so much away
	from so many, and the rewards, taken by the Corporations. As long as
	\textbf{we} have the ability to invent, \textbf{what which was taken} can
	\textbf{not} be kept for long....
	
	To the Makers among us, don't give your \textbf{time,} your
	\textbf{creativity,} your \emph{\textbf{life}} to a Corporation! An
	organization designed for the sole purpose of greed; Designed to take as
	much as possible for itself, to maximize shareholder value! Don't live
	for greed, \textbf{Design for Freedom!} We the Makers have the power to
	build Our Own automated production. \textbf{The power to create abundance!} We the Makers have the power to make this life Free and
	Beautiful, to make this life a wonderful adventure! In the name of
	Community and Free Information let us use this power, let us all unite
	towards a common project. Let us design a free and open source
	production system to provide \textbf{abundance for \emph{all}}\emph{.}
	By the promise of abundance Corporations have risen to power. But they
	lie! They do not fulfill that promise. \textbf{They never will!} Free
	markets free Corporations, but they enslave the people! Now let us
	design a better world, a world of local sustainable automated abundance
	- to do away with greed, with hate and domination. Let us design for a
	world of reason, a world where science and progress will lead to all
	humanity's freedom. \textbf{Makers!} in the name of Freedom and
	Community, \textbf{LET US ALL UNITE!}\footnote{Credit: Charlie Chaplin, Reworked by Kevin Harrington}
}