	\section{What is Property?}
\subsection{ Legal Definitions}

This category is referred to as "Private Property" and is a collection of a few distinct rights. These are the rights enforced by and recognized by law. 

\begin{enumerate}
	
	\item \textbf{Usufruct} - the right to use and receive the value from a piece of the physical world
	
	\item \textbf{Destruction} - the right to destroy a piece of the physical world
	
	\item \textbf{Exclusion} -  the right to exclude others
	
	\item \textbf{Increase (rent)} - the right to receive rents
\end{enumerate}



\subsection{Categories in a Commons}

Within a Commons, once the external entity has been assigned Private Property rights within the law, then that "bubble" can ascribe the rights according to its own rules. The commons can allocate areas of the pieces of the physical world that it manages (the clearly defined boundaries). The allocations can be for consumed aspects (the increase), it can be to assign use terms (Usufruct), and it can determine to what degree exclusion and destruction are used within the commons.


\subsection{Personal Property} The items or space that is exclusively assigned along the legal definition. These can be either private property that came with someone into the commons, or can be the appropriators allocated share of some bounty. 


\subsection{Commons Space} This is the piece of the physical world that may have Usufruct allocated to members, or the public. These generally have the right of destruction held within the commons (for repairs and upgrades). The right to exclude is also held by the commons itself to determine if and when people can or will be excluded. 

\subsection{Public Space} This is space held by the state that assigned property rights. Examples would be the roads, infrastructure and public lands such as parks. 